\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2010-07-25 article.tex
Removed unnecessary details from the outline
Added description and tags in the approach section

  Our data comes from two different sources. The terminology associated with
  pattern movements is from Taekwon-Do ITF Sonkal Praha\footnote{\url{http://sonkal.taekwondo.cz}},
  and the English description of each movement is from the condensed
  encyclopedia\cite{cyclo:con}.

@@

% the approach taken to register and investigate the dataset

% added tags
%   give an overview over (groups of) tags, see movements_with_tags.txt
%     Group of tags
%     Groups of techniques {blocks, strikes, thrusts, punches}
%       height
%       weapon
%       type etc.
%   show an example (chon-ji movement no. 1, for instance)
% divided each pattern into its own text file (./patterns/*)
% modelled the project in the database (./models)
%   explain all attributes etc.
% made a ruby script to parse the text files (link to bootstrap.rb ?)
%   adding the contents into a database using datamapper (orm) (link to datamapper) || populated the database using Datamapper (orm)
%   saving the data into an sqlite3 database for analysis
%

@@

% hva forholder jeg meg til ved utvetydigheter (15-binds vs. *kondenserte*)
% vurderinger på teknikker
% hvorfor er tekniker gruppert slik de er?

>>>>

  Our data comes from two different sources. The terminology associated with
  pattern movements is from Taekwon-Do ITF Sonkal Praha\footnote{\url{http://
  sonkal.taekwondo.cz}}, and the English description of each movement is from
  the condensed encyclopedia\cite{cyclo:con}.

@@

  Each pattern movement is tagged on the basis of their English description
  from the condensed encyclopedia. In addition, suitable tags were attached to
  the dataset while performing the pattern to add necessary details.

  The first movement in Chon-Ji, for instance, is to ``[m]ove the left foot to
  B, forming a left walking stance toward B while executing a low block to B
  with the left forearm.'' Removing the unnecessary parts of the description,
  we're left with:

  \[
    \{left \: walking \: stance, \: low \: block, \: left \: forearm\}
  \]

  Converting the above to tags gives us:

  \[
    \{walking\_stance, left\_stance, low\_technique, left\_technique,
    block, forearm, outer\_forearm, normal\_motion\}
  \]

% why?
%because it to tags means we need to be more specific, so it's easier to
%retrieve movements of same qualities..

% pek på forskjeller mellom tags og bevegelse, hvilke detaljer som blir
% utelatt, detaljer i forhold til diagrammet er ikke tatt med i datasettet

% techniques were grouped

%stance[type, (side)], technique[height,

%stance type, [stance side], technique height, technique side, [direction of
%technique side], technique type, tool group, technique tool,
%[specific technique tool], motion type

%stance (type, [side]), technique (height, side, [direction], type), technique
%(tool group, tool, [specific tool], motion type

%stance type
%stance side (left, right, none (sitting stances for example))
%technique height
%technique side (left, right or both)
%[direction of technique (side_front)]
%technique type (attack or block)
%tool group (forearm, strike, thrust, punch)
%technique tool (outer_forearm, rising_block, front_strike, finger, angle_punch)
%specific technique tool, when needed (side_elbow, double_finger)
%motion type (normal_motion, fast_motion)

%ett eksempel med blokk, pluss ett eksempel med angrep (begge eksemplene bør få
%med de aller fleste momentene nevnt over for å illustrere hva som menes med de
%ulike gruppene)

% added tags
%   give an overview over (groups of) tags, see movements_with_tags.txt
%     Group of tags
%     Groups of techniques {blocks, strikes, thrusts, punches}
%       height
%       weapon
%       type etc.

@@

% hva forholder jeg meg til ved utvetydigheter (15-binds vs. *kondenserte*)
% vurderinger på teknikker

% modelled the project in the database (./models)
%   explain all attributes etc.
% made a ruby script to parse the text files (link to bootstrap.rb ?)
%   adding the contents into a database using datamapper (orm) (link to datamapper) || populated the database using Datamapper (orm)
%   saving the data into an sqlite3 database for analysis
%
